
```{r}
acc <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/fars2017/accident.csv", stringsAsFactors = FALSE)
per <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/fars2017/person.csv", stringsAsFactors = FALSE)

library("tidyverse")
library(maps)
library(ggrepel)
library(mapproj)
```

## Question 1
Shows that the seventh day of the week is the most hazardous and that corresponds to a Saturday.
```{r}
t <- table(acc$DAY_WEEK)
t

which.max(t)
```

## Question 2

```{r}
fatally_hurt <- per %>% filter(INJ_SEV != 0)
head(fatally_hurt)
```

## Question 3
```{r}
mostDang <- per %>% group_by(STATE, MAKE) %>% drop_na %>% select(MAKE, STATE, INJ_SEV) %>% summarise(count=n())%>% group_by(STATE) %>% top_n(1, count)
head(mostDang)
```

## Question 4
```{r}
GLC <- readxl::read_xlsx('C://Users//caitl//Documents//ds202_lab5//GLC.xlsx')
str(GLC)

GLC$`State Code` <- as.numeric(GLC$`State Code`)

danger <- left_join(mostDang, GLC, by=c("STATE"="State Code"))%>% select(STATE, MAKE, count, `State Name`)%>% group_by(STATE, `State Name`) %>% distinct()
danger$`State Name` <- tolower(danger$`State Name`)
danger

states <- map_data("state")
head(states)
states2 <- states %>% group_by(region) %>% summarise(long=mean(long), lat=mean(lat))
head(states2)

dangerMap <- danger %>% left_join(states2, by=c("State Name"="region"))%>% select(STATE, MAKE, count, `State Name`,long, lat)%>%distinct()

dangerMap

ggplot(data=states, aes(x=long, y=lat))+geom_polygon(aes(group=group), color='white')+coord_map()+geom_label_repel(data=dangerMap, aes(label=MAKE), size=2, max.overlaps=Inf)+xlab("Longitude")+ylab("Latitude")+ggtitle("Most Dangerous Car Make by State")
```

The most dangerous vehicle in each state was determined by the number of severe injuries sustained in car accidents based on each car make. The most dangerous car makes seemed to be 20, 12, 49, and 37, with 20 and 12 having been the most dangerous in the most amount of states. The East coast could have more cars of makes 37 and 49 than the rest of the US as those were the most dangerous vehicles in many of the East coast states. 

## Question 5
```{r}
acc_pr <- full_join(acc, per)
head(acc_pr)
```

## Question 6
It seems the day of the week with the most accidents happens on the seventh day (Saturday) with the six day (Friday) being close behind.
Next, the hours with the highest amounts of accidents are the 18th hour and the 17th hour. I.e. 5 and 6 o'clock. These hour tend to be when most people begin their way home from work. The least amount of accidents happened during 99 (unknown time). Excluding this we can see the least amount of accidents during a known time is 4 ergo 4am. Most people are asleep at this time. Finally, it shows that men are twice as likely to get into accidents as women are.
```{r}
day_week <- table(acc_pr$DAY_WEEK)
day_week

hour <- table(acc_pr$HOUR)
hour

sex <- table(acc_pr$SEX)
sex

ggplot(acc_pr, aes(DAY_WEEK)) + geom_bar(fill="red")

ggplot(acc_pr, aes(HOUR)) + geom_bar(width=0.5, fill="blue")

ggplot(acc_pr, aes(SEX)) + geom_bar()
```